\TheTitle

### 2015-08-15 linvis.tex
Implementation Details: Database Tables
Working on describing the design of the database. Still need to talk about the
heuristics used for converting the DAG into a tree structure.

Tool Implementation Details:
	Web Server: Nginx, Flask, postgresql
	Database: 5 tables

>>>>

The database itself is broken down into 5 main tables; commits, filesmod, logs,
pathtomerge, and releases. Commits contains most of the metadata for each
commit, it contains the author, the authored date, and committer, the commit
date, a boolean saying what is a merge, and the diff. Filesmod contains the
information on what files were modified for the commits. Since a file may be
modified by multiple commits, and a commit may be modifying multiple files, we
can do one of two things for the primary key. We could use both the filename
and the commit id as the primary key, but we just use an index. The filesmod
table contains the filename, the commit id, the number of lines added, and the
number of lines removed. Trivially, it contains the index, but that isn't
necessary for anything beyond the primary key. Logs contains the information
for each commit log, this is the one-liner preview message and the full
message. Pathtomerge is the important table. Pathtomerge contains the commit
id, the number of merges between the commit and the top-level merge with the
kernel, the next merge in the merge path up to the top-level merge with the
kernel, the top-level merge into the kernel, and when it get merged into the
kernel. The information in this table must be generated periodically by the
server because we are unable to generate the tree structure correctly straight
from the information stored by git. Pathtomerge does not contain any top-level
merges, as these will never have a next merge in the tree, since we are only
storing the parents and not the children, storing the top-level merge is
redundant and unnecessary. The releases table stores the release information.
It contains the version name, whether the version is a candidate release or a
real release, the previous version, the previous non-candidate release version
the previous version commit id, the previous non-candidate release version
commit id, and the commit id of this version. The version commit id represents
the last top-level merge into the version of the kernel. Using this and the
commits table, we are able to determine the release date of any version of the
kernel. Then using the previous release date, we can find the range of dates
where valid top-level merges are found for that version.

\evantodo{Talk a bit about the heuristics used for building the tree from the
DAG}
